Family Fortunes: A Quantitative Analysis of the Early Iron Age Cemeteries at Knossos, Crete

### 2019-05-20 analysis/paper/paper.Rmd
First draft analysis

```{r dimensions boxplots}

@@

```{r}

@@

```{r}

@@

```{r gini}

@@

```{r}
pots$group<-ifelse(pots$tomb=="P"|pots$tomb=="292"|pots$tomb=="75"|pots$tomb=="107"|pots$tomb=="285"|pots$tomb=="II"|pots$tomb=="218","A","B")

@@

ggarrange(potcompKNC,potcompFOR,potcomptop7,ncol=3,common.legend =TRUE,legend="bottom")
```

@@

```{r }
tombs$group<-factor(tombs$group,levels=c("A","B"))
total_object<-ggplot(subset(tombs,est_burials>1),aes(total_object, fill=group))+geom_histogram()+
  theme_bw()+theme(legend.title=element_blank(),
               text=element_text(family="Garamond", size=12))+
                 labs(x="Total Non-Ceramic Finds", y="Number of Tombs")+
                  scale_fill_brewer(palette = "Set2",labels=c(" 7 Tombs  ", " Other Tombs"))+
                    scale_y_continuous(expand=c(0,0))+scale_x_continuous(expand=c(0,0))
total_metal<-ggplot(subset(tombs,est_burials>1),aes(weapon, fill=group))+geom_histogram()+
  theme_bw()+theme(legend.title=element_blank(),
               text=element_text(family="Garamond", size=12))+
                 labs(x="Total Metal Artefacts", y="Number of Tombs")+
                  scale_fill_brewer(palette = "Set2",labels=c(" 7 Tombs  ", " Other Tombs"))+
                    scale_y_continuous(expand=c(0,0))+scale_x_continuous(expand=c(0,0))
total_import<-ggplot(subset(tombs,est_burials>1),aes(total_import, fill=group))+geom_histogram()+
  theme_bw()+theme(legend.title=element_blank(),
               text=element_text(family="Garamond", size=12))+
                 labs(x="Total Imports", y="Number of Tombs")+
                  scale_fill_brewer(palette = "Set2",labels=c(" 7 Tombs  ", " Other Tombs"))+
                    scale_y_continuous(expand=c(0,0))+scale_x_continuous(expand=c(0,0))

@@

ggarrange(total_import,total_weapon,total_object,importsbyburial,weaponbyburial,objectsbyburial,ncol=3,nrow=2,common.legend = TRUE,legend="bottom")
```

>>>>

```{r dimensions boxplots, fig.dim=c(8,4),dpi=300}

@@

```{r imports, fig.dim=c(6,4),dpi=300}

@@

```{r bigbox, fig.dim=c(8,4),dpi=300}

@@

```{r gini, fig.dim=c(7,4),dpi=300}

@@

```{r comps, fig.dim=c(8,4),dpi=300}
pots$group<-ifelse(pots$tomb=="P"|pots$tomb=="292"|pots$tomb=="75"|pots$tomb=="107"|pots$tomb=="285"|pots$tomb=="II"|pots$tomb=="218","A","B")

@@

ggarrange(potcompKNC,potcompFOR,potcomptop7,ncol=3,common.legend =TRUE,legend="bottom")

spearmanobjectspots<-cor(tombs$total_object,tombs$total_pottery,method="spearman")
```

@@

```{r hists, fig.dim=c(8,4),dpi=300}
tombs$group<-factor(tombs$group,levels=c("A","B"))
total_object<-ggplot(subset(tombs,est_burials>1),aes(total_object, fill=group))+geom_histogram()+
  theme_bw()+theme(legend.title=element_blank(),
               text=element_text(family="Garamond", size=12))+
                 labs(x="Total Non-Ceramic Finds", y="Number of Tombs")+
                  scale_fill_brewer(palette = "Set2",labels=c(" 7 Tombs  ", " Other Tombs"))+
                    scale_y_continuous(expand=c(0,0))+scale_x_continuous(expand=c(0,0))
total_metal<-ggplot(subset(tombs,est_burials>1),aes(weapon, fill=group))+geom_histogram()+
  theme_bw()+theme(legend.title=element_blank(),
               text=element_text(family="Garamond", size=12))+
                 labs(x="Total Metal Artefacts", y="Number of Tombs")+
                  scale_fill_brewer(palette = "Set2",labels=c(" 7 Tombs  ", " Other Tombs"))+
                    scale_y_continuous(expand=c(0,0))+scale_x_continuous(expand=c(0,0))
total_import<-ggplot(subset(tombs,est_burials>1),aes(total_import, fill=group))+geom_histogram()+
  theme_bw()+theme(legend.title=element_blank(),
               text=element_text(family="Garamond", size=12))+
                 labs(x="Total Imports", y="Number of Tombs")+
                  scale_fill_brewer(palette = "Set2",labels=c(" 7 Tombs  ", " Other Tombs"))+
                    scale_y_continuous(expand=c(0,0))+scale_x_continuous(expand=c(0,0))

@@

ggarrange(total_import,total_metal,total_object,importsbyburial,metalbyburial,objectsbyburial,ncol=3,nrow=2,common.legend = TRUE,legend="bottom")
```
